A Graph-based Framework for Coverage Analysis in Autonomous Driving

### 2025-10-13 article/article.tex

@@

\begin{itemize}
    \item In autonomous driving, coverage analysis is a crucial step to ensure the safety and reliability of the system.
    \item In most situations, coverage arguments are collected either per coverage factor, or maybe up to 2 or 3 factor interactions.
    \item See for example \cite{foretellix2019} for an production grade implementation of state of the art coverage analysis.
    \item In contrast to existing approaches, this paper proposes a graph-based framework for coverage analysis.
    \item There are already other graph-based approaches for analysing and representing traffic scenes, see for example \cite{behr2021graph}.
    \item However, the work in that paper is not specifically focused on coverage analysis.
    \item Hence in this paper, graph based traffic scene representations are utilized for coverage analysis.
    \item This paper is structured as follows:
    \begin{itemize}
        \item In the first section, xxx
    \end{itemize}
\end{itemize}

\cite{wagner2022odd}

\cite{arzamasov2021data}

\section{exsting coverage and analysis approaches}

@@

\section{Defining a traffic scene graph}

\cite{behr2021graph}

@@

\cite{pek2019generating}

\subsection{time based graph representations}

@@

\section{Create subgraphs for coverage analysis}

@@

\section{Implementation of Graph Embeddings for Traffic Scene Analysis}

@@

\section{Application}

>>>>

test3

@@

In autonomous driving, coverage analysis is a crucial step to ensure the safety and reliability of the system.
In most situations, coverage arguments are collected either per coverage factor, or maybe up to 2 or 3 factor interactions.
See for example \cite{foretellix2019} for an production grade implementation of state of the art coverage analysis.
In contrast to existing approaches, this paper proposes a graph-based framework for coverage analysis.
There are already other graph-based approaches for analysing and representing traffic scenes.
However, the work in that paper is not specifically focused on coverage analysis.
Hence in this paper, graph based traffic scene representations are utilized for coverage analysis.

This paper is structured as follows: In chapter \ref{chapter:existing_approaches}, existing coverage and analysis approaches are discussed.
The basis for the following chapters is layed in chapter \ref{chapter:defining_a_traffic_scene_graph}. Afterwards, two coverage approaches 
using the traffic scene graphs are discussed in chapter \ref{chapter:create_subgraphs_for_coverage_analysis} and 
chapter \ref{chapter:implementation_of_graph_embeddings_for_traffic_scene_analysis}.
Finally, the developed methods are applied to Carla and Argoverse 2.0 data in chapter \ref{chapter:application} 
followed by a short summary and outlook.

\section{Existing coverage and analysis approaches}
\label{chapter:existing_approaches}

@@

\section{Defining a traffic scene graph}
\label{chapter:defining_a_traffic_scene_graph}

still to be added: \url{https://sagroups.ieee.org/adwg/wp-content/uploads/sites/661/2024/10/ADWG_STV2_whitepaper.pdf}

still to be added: \url{https://www.vvm-projekt.de/securedl/sdl-eyJ0eXAiOiJKV1QiLCJhbGciOiJIUzI1NiJ9.eyJpYXQiOjE3NDc2OTIxNjgsImV4cCI6MTc0Nzc4MjE2OCwidXNlciI6MCwiZ3JvdXBzIjpbMCwtMV0sImZpbGUiOiJmaWxlYWRtaW4vdXNlcl91cGxvYWQvVlZNZXRob2Rlbl9adXNhbW1lbmZhc3NlbmRlcl9BYnNjaGx1c3NiZXJpY2h0X3YxLjBfenVyX1Zlc_f9d402f084002b57/VVMethoden_Zusammenfassender_Abschlussbericht_v1.0_zur_Veroeffentlichung.pdf}

@@

\subsection{time based graph representations}
The graph creation strategy described above is assuming to create a graph for a single timestep. One possible 
extension is to create a graph which contains information for multiple timesteps.

\begin{itemize}
    \item create a graph for multiple timesteps
    \item create a joint set of nodes. 
    \item For each time step, determine the corresponding edges.
    \item Add all edges to the graph, resulting in a di-graph, which can contain for a pair of nodes as many edges as there are time steps.
\end{itemize}

This extension allows the graph to easily represent changing states, e.g. the relationship between two vehicles 
changes from neighbor to leading vehicle, i.e. a cut in happened. One important special case for this type of processing is 
to handle actors, which are not present in all time steps, i.e. they appear and disappear during the time window. Especially 
if node attributes are used in the processing, a suitable imputation strategy is necessary to avoid 
non-equal dimensions of tensors for node attributes.

The methods derived in the following chapters can be applied to this extended graph representation as well, even though 
the focus in this paper will be on single timestep graphs.

@@

\section{Create subgraphs for coverage analysis}
\label{chapter:create_subgraphs_for_coverage_analysis}

@@

\section{Implementation of Graph Embeddings for Traffic Scene Analysis}
\label{chapter:implementation_of_graph_embeddings_for_traffic_scene_analysis}

@@

\section{Application}
\label{chapter:application}
